Learning constraints in tabular data

### 2016-05-12 Paper/ECAI/tabular.tex
title of the table

\begin{table}
  \centering
  \begin{tabular}{lll}
    & \textbf{Total} & \textbf{Average per spreadsheet} \\
    \textbf{Constraints} & $93$ & $2.91$ \\
    \textbf{Accuracy} & $96.77\%$ & $94.27\%$ \\
    \textbf{Redundant} & $23.14\%~(28)$ & $8.33\%~(0.88)$ \\
    \textbf{Speed (s)} & ${\runtotal}s \pm {\runtotalstd}s$ & ${\runfile}s \pm {\runfilestd}s$
  \end{tabular}
  \caption{Overview evaluation on essential constraints}
\end{table}
\samuel{Expand summary}

@@

\section{Applications}\label{sec:applications}
In this section we will illustrate how various motivating applications could be realized using our system.

>>>>

\begin{table}
  \centering
  \begin{tabular}{lll}
    & \textbf{Total} & \textbf{Average per spreadsheet} \\
    \textbf{Constraints} & $93$ & $2.91$ \\
    \textbf{Accuracy} & $96.77\%$ & $94.27\%$ \\
    \textbf{Redundant} & $23.14\%~(28)$ & $8.33\%~(0.88)$ \\
    \textbf{Speed (s)} & ${\runtotal}s \pm {\runtotalstd}s$ & ${\runfile}s \pm {\runfilestd}s$
  \end{tabular}
  \caption{Overview evaluation on essential constraints of the collected Spreadsheet dataset}
\end{table}
\samuel{Expand summary}

@@

\section{Applications}\label{sec:applications}
In this section, we illustrate how various motivating applications could be realized using our system.
